The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-07-16 article.tex
Writing more content

@@

@@

  Initially done with DocCheck, replaced by OpenJavaDocCheck ...

  \subsubsection*{Unit testing}

>>>>

  The SMILES parsing has been replaced code in the external Beam project~\cite{Beam}.
  This BSD-licensed SMILES parser is a complete implementation of the SMILES
  and OpenSMILES specifications by one of the authors, and is independent of
  the CDK library. The SmilesParser API uses this library underneath, and the
  Beam API is hidden by this class.

@@

  Aromaticity has seen many definitions in the past and for cheminformatics it
  frequently is algorithmically defined. The outcome of an aromaticity calculation
  depends on a number of atom type features and heuristics, which in literature
  often are not well defined. Based on this information several different
  algorithmic definitions of aromaticity can be defined. Older CDK versions had
  various models implemented and the code was scattered throughout the library.
  This was unified resulting in a three models, of which two are based on the
  CDK atom typer, to provide the number of electrons donated by each atom to
  the delocalized $\pi$ system. The difference between these two models is
  how double bonds pointing outwards from a ring are contributing.

  The current CDK version further generalizes the idea that aromaticity is a
  model, and provides an API that allows you to select out of various options
  providing greater interoperability with other toolkits. The new
  Aromaticity class allows to build a custom model by selecting and combining
  options. For example, to reproduce the functionality of the previous
  CDKAromaticity class:

\begin{verbatim}
Aromaticity aromaticity = new Aromaticity(
  ElectronDonation.cdk(), Cycles.cdkAromaticSet()
);
\end{verbatim}

Here, the CDK model for counting donated electrons is used, as the ring systems
the CDK previously included in aromaticty counting, which was limited in the 
number of fused rings systems. However, an alternative aromaticity calculator
that does consider all possible ring systems can now be easily created with:

\begin{verbatim}
Aromaticity aromaticity = new Aromaticity(
  ElectronDonation.cdk(), Cycles.all()
);
\end{verbatim}

@@

  The quality of JavaDoc of the CDK was originally tested with DocCheck, and
  later replaced by a custom written tool called OpenJavaDocCheck. With the move
  to Maven (explained elsewhere) which does not have integration for this tool,
  we adopted CheckStyle (\url{http://checkstyle.sourceforge.net/}). This tool
  reports about missing documentation and on documentation which is not properly
  annotated in the Java source files.

  \subsubsection*{Testing}

  Years of development of the CDK library has resulted in a large suite of
  tests of various kinds. This include unit tests, which test core APIs, and
  functional testing, which test higher level functionality of the CDK. The
  latter include tests if algorithm implementations calculate the expected
  values, but also contain integrated tests, which involve more than one
  algorithms, such as SMILES parsing.
